Incentivizing Exploration with Unbiased History

### 2018-10-31 2level.tex
update figures
remove "randomness" in the policy description, our info graph is deterministic and public knowledge

%!TEX root = main.tex
\section{Warm-up:  2-Level Explore-then-Exploit Policy}
\swedit{Now we provide a simple policy that can incentivize the agents
  to perform non-adaptive exploration and achieve a regret rate of
  $\tilde O(T^{2/3})$. The policy essentially follows the
  ``explore-then-exploit'' paradigm and consists of two phases, which can
  be described as a two-level information graph (as shown in
  Figure~\ref{fig:2level}).  In the first level, we perform
  exploration by simulating $T_1$ independent runs of \ALGG of $\GdT$
  rounds. This is done by randomly dividing the first $T_1 \cdot \GdT$
  agents into $T_1$ groups of equal size and allowing each agent to only observe
  the history of all previous agents in the same group.  In the second
  level, we ``exploit'' by showing all the remaining agents the entire
  history of first phase.

@@

\begin{figure}[H]
\centering
\begin{tikzpicture}  
 \filldraw[fill=blue!20!white]
 (0,2)--(10,2)--(10,3)--(0,3)--cycle;
  \filldraw[fill=red!20!white]
  (0,0)--(1,0)--(1,1)--(0,1)--cycle;
  \draw[dashed] (0.5,1)--(5,2);
  \filldraw[fill=red!20!white]
  (1,0)--(2,0)--(2,1)--(1,1)--cycle;
  \draw[dashed] (1.5,1)--(5,2);
  \filldraw[fill=red!20!white]
  (2,0)--(3,0)--(3,1)--(2,1)--cycle;
  \draw[dashed] (2.5,1)--(5,2);
  \filldraw[fill=red!20!white]
  (3,0)--(4,0)--(4,1)--(3,1)--cycle;
  \draw[dashed] (3.5,1)--(5,2);
  \filldraw[fill=red!20!white]
  (9,0)--(10,0)--(10,1)--(9,1)--cycle;
  \draw[dashed] (9.5,1)--(5,2);
  \node at(5,0.5){$\cdots$};
  \node at(6,0.5){$\cdots$};
  \node at(7,0.5){$\cdots$};
  \node at(8,0.5){$\cdots$};
  \node at(5,2.5){$T -T_1 \cdot \GdT$};
  \node at(0.5,0.5){$\GdT$};
  \node at(1.5,0.5){$\GdT$};
  \node at(2.5,0.5){$\GdT$};
  \node at(3.5,0.5){$\GdT$};
  \node at(9.5,0.5){$\GdT$};
  \node at(-1,0.5){\textbf{Level 1}};
  \node at(-1,2.5){\textbf{Level 2}};
  \draw[->] (11,0)--(11,3);
  \node at(11.5,1.5)[ rotate=90]{Time};

>>>>

%!TEX root = main.tex
\section{Warm-up:  2-Level Explore-then-Exploit Policy}
\swedit{Now we provide a simple policy that can incentivize the agents
  to perform non-adaptive exploration and achieve a regret rate of
  $\tilde O(T^{2/3})$. The policy essentially follows the
  ``explore-then-exploit'' paradigm and consists of two phases, which can
  be described as a two-level information graph (as shown in
  Figure~\ref{fig:2level}).  In the first level, we perform
  exploration by simulating $T_1$ independent runs of \ALGG of $\GdT$
  rounds. This is done by dividing the first $T_1 \cdot \GdT$
  agents into $T_1$ groups of equal size and allowing each agent to only observe
  the history of all previous agents in the same group.  In the second
  level, we ``exploit'' by showing all the remaining agents the entire
  history of first phase.

@@

\begin{figure}[H]
\centering
\begin{tikzpicture}  
 \filldraw[fill=blue!20!white]
 (0,2)--(10,2)--(10,3)--(0,3)--cycle;
  \filldraw[fill=red!20!white]
  (0,0)--(1,0)--(1,1)--(0,1)--cycle;
  \draw (0.5,1)--(5,2);
  \filldraw[fill=red!20!white]
  (1,0)--(2,0)--(2,1)--(1,1)--cycle;
  \draw (1.5,1)--(5,2);
  \filldraw[fill=red!20!white]
  (2,0)--(3,0)--(3,1)--(2,1)--cycle;
  \draw(2.5,1)--(5,2);
  \filldraw[fill=red!20!white]
  (3,0)--(4,0)--(4,1)--(3,1)--cycle;
  \draw(3.5,1)--(5,2);
  \filldraw[fill=red!20!white]
  (9,0)--(10,0)--(10,1)--(9,1)--cycle;
  \draw(9.5,1)--(5,2);
  \node at(5,0.5){$\cdots$};
  \node at(6,0.5){$\cdots$};
  \node at(7,0.5){$\cdots$};
  \node at(8,0.5){$\cdots$};
  \node at(5,2.5){$T -T_1 \cdot \GdT$};
  \node at(0.5,0.5){$\GdT$};
  \node at(1.5,0.5){$\GdT$};
  \node at(2.5,0.5){$\GdT$};
  \node at(3.5,0.5){$\GdT$};
  \node at(9.5,0.5){$\GdT$};
  \node at(-1,0.5){\textbf{Level 1}};
  \node at(-1,2.5){\textbf{Level 2}};
  \draw[->] (11,0)--(11,3);
  \node at(11.5,1.5)[ rotate=90]{Time};
